\ldots

### 2016-02-12 paper.tex
Compositional experiments

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
  \caption{\textbf{Shifted PMI mean performance and variance.}}
  \label{fig:ppmi-performance}
\end{figure*}

We start with exploring the performance of SPMI, in particular \SPMI/. Figure~\ref{fig:ppmi-performance} shows the mean performance and the variance of the SPMI models grouped by vector dimensionality and frequency on the SimLex-999 dataset.

Average \SPMI/ performance increases for the dimensionality values in the range of 1K to 10K. After 10K dimensions, the average \SPMI/ performance degrades. \SPMI/ score variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards. This suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.

@@

>>>>

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
  \caption{\textbf{Shifted PMI mean performance and variance.}}
  \label{fig:ppmi-performance}
\end{figure*}

@@

Figure~\ref{fig:ppmi-performance} shows the mean performance and the variance of the SPMI models grouped by vector dimensionality and frequency on the SimLex-999 dataset.

We start with exploring the performance of \SPMI/. Average \SPMI/ performance increases for the dimensionality values in the range of 1K to 10K. After 10K dimensions, the average \SPMI/ performance degrades. \SPMI/ score variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards. This suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.

@@

In compositional experiments, the main goal is to study compositional operators rather than special weighting schemes, therefore we will see the weighting scheme as another hyperparameter that is being optimized and study compositional operators in isolation.

Figure~\ref{fig:emnlp13-ppmi-performance} shows SPMI's average performance and evaluation score variance on the KS14 dataset.

Addition has the highest average performance and a relatively low variance. Multiplication, shows lowest average performance, but the result variance is much higher than addition. Kronecker exhibits behavior similar to multiplication.

\subsection{Addition}
\label{sec:addition}
